Detecting Facial Expressions in Video Stills from Professional Tennis Matches

### 2018-01-17 paper/paper.Rmd
accessory changes
Accessories tables reworked

Figure \@ref(fig:timeFigure) displays the distribution of processing time required by the APIs for each image, as a violin plot (REF). Both Microsoft and Google had few images where they had taken a significant amount of time to complete, and these were removed from this plot due to concerns regarding the network. The times taken to search are quite variable between APIs, with Skybiometry consistently spending less time than other APIs. Microsoft and Google's times vary regardless of the number of faces found.

@@

```{r glasses, fig.cap = "\\label{tab:glasses}", digit=3}

ManFaces %>% count(glasses) %>%
  tally() -> ManGlasses

aminFaces %>% filter(matchesManual==TRUE) -> afm

@@

glassesdf <- rbind(c(" ", "Animetrics","Google","Microsoft","Skybiometry"),
c("No", 
  round(glassesTab[1,2]/glassesTab[1,1],2),
  round(glassesTab[1,3]/glassesTab[1,1],2),
  round(glassesTab[1,4]/glassesTab[1,1],2),
  round(glassesTab[1,5]/glassesTab[1,1],2)),
c("Yes", 
  round(glassesTab[2,2]/glassesTab[2,1],2),
  round(glassesTab[2,3]/glassesTab[2,1],2),
  round(glassesTab[2,4]/glassesTab[2,1],2),
  round(glassesTab[2,5]/glassesTab[2,1],2)))
```

\begin{table}[ht]
\centering
%\parbox{.5\linewidth}{
\caption{Conditional proportions of faces of players wearing glasses or not, captured by the different software, in comparison to the manually tagged faces. API's unaffected glasses will have similar proportions for both categories. Animetrics had the biggest proportion difference, and thus, most affected. Google is the least affected.} 
\label{tab:glasses}
\begin{tabular}{|l|rrrr|}
\hline 
 & Animetrics & Google & Microsoft & Skybiometry\\ 
\hline
Glasses & 0.08 & 0.43 & 0.14 & 0.12 \\
No Glasses & 0.21 & 0.60 & 0.26 & 0.23\\
\hline
\end{tabular}
\end{table}

>>>>

Figure \@ref(fig:timeFigure) displays the distribution of processing time required by the APIs for each image, as a violin plot [@Violin]. Both Microsoft and Google had few images where they had taken a significant amount of time to complete, and these were removed from this plot due to concerns regarding the network. The times taken to search are quite variable between APIs, with Skybiometry consistently spending less time than other APIs. Microsoft and Google's times vary regardless of the number of faces found.

@@

```{r glasses, fig.cap = "\\label{tab:glasses}", digit=3}
aminFaces %>% filter(matchesManual==TRUE) -> afm

@@

glassesdf <- cbind(c(" ", "Animetrics","Google","Microsoft","Skybiometry"),
                   c("Yes", 
  round(glassesTab[2,2]/glassesTab[2,1],2),
  round(glassesTab[2,3]/glassesTab[2,1],2),
  round(glassesTab[2,4]/glassesTab[2,1],2),
  round(glassesTab[2,5]/glassesTab[2,1],2)),
c("No", 
  round(glassesTab[1,2]/glassesTab[1,1],2),
  round(glassesTab[1,3]/glassesTab[1,1],2),
  round(glassesTab[1,4]/glassesTab[1,1],2),
  round(glassesTab[1,5]/glassesTab[1,1],2))
)

# Headwear
table(afm$visorhat, afm$type) %>% as.matrix() -> headwearTab

headweardf <- cbind(c(" ", "Animetrics","Google","Microsoft","Skybiometry"),
                   c("Yes", 
  round(headwearTab[2,2]/headwearTab[2,1],2),
  round(headwearTab[2,3]/headwearTab[2,1],2),
  round(headwearTab[2,4]/headwearTab[2,1],2),
  round(headwearTab[2,5]/headwearTab[2,1],2)),
c("No", 
  round(headwearTab[1,2]/headwearTab[1,1],2),
  round(headwearTab[1,3]/headwearTab[1,1],2),
  round(headwearTab[1,4]/headwearTab[1,1],2),
  round(headwearTab[1,5]/headwearTab[1,1],2))
)
```

\begin{table}[htp]
%\parbox{.5\linewidth}{
\caption{Conditional proportions of faces of players wearing glassesor headwear or not, captured by the different software, as a proportion of the manually tagged faces. API's unaffected by glasses will have similar proportions for both categories. Animetrics had the biggest proportion difference, and thus, most affected. Google is the least affected.}
\bigskip
\label{tab:glassesheadwear}
\centering
\begin{tabular}{|l|rr|rr|}  \hline
& \multicolumn{2}{r|}{Headwear}&\multicolumn{2}{r|}{Glasses}\\\cline{2-5}
API & Yes & No & Yes & No \\\hline
Google & 0.48 & 0.69 & 0.43 & 0.60 \\
Microsoft & 0.19 & 0.32 & 0.14 & 0.26 \\
Skybiometry & 0.16 & 0.28 & 0.12 & 0.23 \\
Animetrics & 0.11 & 0.27 & 0.08 & 0.21 \\\hline
\end{tabular}
\end{table}
